Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-03-06 docs/Truman/LocalConservation/paper.tex
Fixed results with robust norm and conservation.

As we refine, the three results, nonconservative with graph or robust norm,
and conservative with graph norm converge to a an essentially identical
solution (to the eyeball norm), as represented by
Figure~\ref{fig:confusionGraph8c}. However, the conservative formulation with
the robust norm seems to exhibit some noise at the right wall as seen in
Figure~\ref{fig:confusionRobust8c}.

@@

If we zoom in on one of the noisy areas, as we do in
Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
and undershoots on the order of -13, where the exact solution varies between 0
and 1. The cause of these overshoots and undershoots is a little mystery,
especially because they don't show up until 8 refinement steps in. We will
explore this problem a little more when we look at the wedge problem.

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
\caption{Zoomed in conservative skewed convection-diffusion problem after 8
refinements}
\label{fig:confusionRobust8c_zoom}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/graphFlux.pdf}
\caption{With graph norm}
\label{fig:discontinuousGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/robustFlux.pdf}
\caption{With robust norm}
\label{fig:discontinuousRobustFlux}
\end{subfigure}
\caption{Flux imbalance in discontinuous source solutions}
\label{fig:discontinuous_flux}
\end{figure}

>>>>

As we refine, the three results, nonconservative with graph or robust norm,
and conservative with graph norm converge to a an essentially identical
solution (to the eyeball norm), as represented by
Figure~\ref{fig:confusionGraph8c}.

% However, the conservative formulation with
% the robust norm seems to exhibit some noise at the right wall as seen in
% Figure~\ref{fig:confusionRobust8c}.

@@

% If we zoom in on one of the noisy areas, as we do in
% Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
% and undershoots on the order of -13, where the exact solution varies between 0
% and 1. The cause of these overshoots and undershoots is a little mystery,
% especially because they don't show up until 8 refinement steps in. We will
% explore this problem a little more when we look at the wedge problem.
% 
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
% \caption{Zoomed in conservative skewed convection-diffusion problem after 8
% refinements}
% \label{fig:confusionRobust8c_zoom}
% \end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/graphFlux.pdf}
\caption{With graph norm}
\label{fig:discontinuousGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/robustFlux.pdf}
\caption{With robust norm}
\label{fig:discontinuousRobustFlux}
\end{subfigure}
\caption{Flux imbalance in discontinuous source solutions}
\label{fig:discontinuous_flux}
\end{figure}
